### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Final Doc Almost Fin

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finporta.png}
  \caption{Main Portal Asset}
\end{subfigure}%
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finportb.png}
  \caption{Tutorial Specific Re-colouration}
\end{subfigure}
\caption{Finalised Portal Assest}
\label{portals}
\end{figure}

\noindent \textbf{Moving Platforms}\\
This script works similarly to the rotation script as instead of rotating the object , this script moves an object between two points in a scene. This script makes use of two Empty GameObjects, that being a GameObject with only positional and rotational information without any assets attached, as the two points a GameObject will be moved between. The GameOjbect being moved has its' position updated constantly along the path using the \texttt{Lerp()} function which places a GameObject on a path between two points depending on a decimal percentage value. When the GameObject reaches a point, it moves back in the opposite direction  towards the other. This process is repeated infinitely.
\\\\
This script could also be used on any GameObject, such as with the Portal Prefab, but was origionally intended for moving platforms only. As such, the player movement script was updated to include the implementation of a platform moving the Player with it. This was accomplished by adding a Tag to any GameObject which is intended as a platform and 
\\\\
\textbf{Ending a Level}\\

\textbf{Tutorial Level Development}\\

%Full Level
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/fullplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/full.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Full Level (Tutorial)}
\end{figure}

%Hub
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/hubplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/hub.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Hub Room}
\end{figure}

%Platform
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/platformplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/platform.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Platforming Tutorial}
\end{figure}

%WallRun
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/wallplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/wall.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Wall Running Tutorial}
\end{figure}

%Throw
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/throwplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/throw.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Throw Tutorial}
\end{figure}

%Mcap
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/mcapplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/mcap.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Movement Tutorial}
\end{figure}

%Enemy
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/enemyplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/enemy.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Enemy Tutorial}
\end{figure}

\textbf{Pause Menu}\\

@@

>>>>

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finporta.png}
  \caption{Main Portal Asset}
\end{subfigure}%
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finportb.png}
  \caption{Tutorial Specific Re-colouration}
\end{subfigure}
\caption{Finalised Portal Prefab}
\label{portals}
\end{figure}

\noindent \textbf{Moving Platforms}\\
This script works similarly to the rotation script as instead of rotating the object , this script moves an object between two points in a scene. This script makes use of two Empty GameObjects, that being a GameObject with only positional and rotational information without any assets attached, as the two points a GameObject will be moved between. The GameOjbect being moved has its' position updated constantly along the path using the \texttt{Lerp()} function which places a GameObject on a path between two points depending on a decimal percentage value. When the GameObject reaches a point, it moves back in the opposite direction  towards the other. This process is repeated infinitely.
\\\\
This script could also be used on any GameObject, such as with the Portal Prefab, but was originally intended for moving platforms only. As such, the player movement script was updated to include the implementation of a platform moving the Player with it. This was accomplished by adding a Tag to any GameObject which is intended as a platform and in the player movement script having a function, \texttt{OnPlatform()}, return a boolean value as with \texttt{OnFloor()} and \texttt{OnSlope()}. When true, the raycast used to determine the boolean is also used to get the GameObject platform and apply a subtle force in the direction of the platform.
\\\\
\textbf{Ending a Level}\\
This script is used on the completion of a level to load the next level in the gameplay sequence. This is done using the collider of the ball GameObject and Unity's SceneManagement library.
\\\\
To progress to the next level, the user must throw the ball GameObject into the designated end goal GameObject and once the \texttt{OnTriggerEnter()} triggers it calls the function \texttt{nextLevel()} which completes a check to identify which scene is loaded and if it is one that has a next level after it, that next level is loaded. This also makes use of the build index of each scene.
\newpage
\noindent \textbf{Tutorial Level Development}\\
This next section details the development of the tutorial level. This includes level design plans and screenshots of the final version of each section of the level. Each section of the tutorial was designed in such a way that it would teach the user the various mechanics implemented in the game.
\\\\
The first provisional plan made was for the entire level in a high level overview of what would be handled and the general layout of where. This includes laying out each individual rooms location in relation to the level as well the beginning and end points. This is shown in Figure \ref{full}.
%Full Level
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/fullplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/full.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Full Level (Tutorial)}
\label{full}
\end{figure}

\noindent The next piece of the level to be designed was the so-called Hub Room. This is the section in the level where the user partakes in the various tutorials. The incorporation of portals was intended from the beginning but for a length of time, the hub room made use of the drop-zones as shown in Figure \ref{hub}. Nonetheless, once the necessary scripts were developed, the portal prefab was developed and consequently incorporated.

%Hub
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/hubplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/hub.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Hub Room}
\label{hub}
\end{figure}

\noindent The platforming tutorial was designed as a tower to illustrate the vertical movement capabilities of the player and the movement script. This tutorial made use of moving platforms and most of the player movement script movement-based functions - i.e. \texttt{Jump()} and \texttt{Crouch()}. The goal of this tutorial was to climb the tower and drop down the centre towards a portal. Figure \ref{platty} shows the plan and final implementation of this section.

%Platform
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/platformplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/platform.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Platforming Tutorial}
\label{platty}
\end{figure}

\noindent Wallrunning was also added to the player movement script during this development phase. This makes use of the orientation GameObject mentioned earlier as well as two raycasts to determine if the player is next to a wall and can wallrun. Furthermore, a player can only wall run if the function \texttt{OnFloor()} returns false, that is if the player is next to a wall and is not on the floor. The basic goal of this tutorial is to reach the other side of the room by using the provided walls. If a player were to fall off while attempting this they would be teleported to the nearest floor and given the chance to try again - this being another use of the teleport script. Once the player reaches the other side and collides with the particle system the door to the portal in the room is moved and a bridge is brought into the room if the user does not want to wallrun back across the room. Figure \ref{wallrun} illustrates the plan and final implementation of this.

%WallRun
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/wallplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/wall.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Wall Running Tutorial}
\label{wallrun}
\end{figure}

\noindent The next tutorial is that of throwing. This tutorial makes heavy use of the teleport script in multiple forms. The first obstacle is a set of barriers that will be moved when hit with the ball GameObject. The second is to hit a moving target upon which the player will be moved to the next section of this tutorial. The last task is to hit a stationary target which the user must read the sign near it and solve the riddle. The player must jump off the ledge and turn around to hit the target. Before the target is hit, once the player hits the floor they are teleported back to the top of the ledge. Once the target is hit, the player is no longer teleported up and a wall is removed revealing a portal; to conclude this tutorial. Figure \ref{throw} shows the plan and finalisation of this section.

%Throw
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/throwplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/throw.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Throw Tutorial}
\label{throw}
\end{figure}

%Mcap
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/mcapplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/mcap.png}
  \caption{Screenshot in Artefact}
\end{subfigure}
\caption{Layout of Movement Tutorial}
\label{moves}
\end{figure}

%Enemy
\begin{figure}[H]
\centering
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/enemyplan.png}
  \caption{Provisional Plan}
\end{subfigure}%
\begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/enemy.png}
  \caption{Screenshot in Unity Editor}
\end{subfigure}
\caption{Layout of Enemy Tutorial}
\label{enemy}
\end{figure}

\noindent \textbf{Pause Menu}\\
The last feature to be added to the game was the implementation of a pause menu. This included a script to handle the toggling of sound on a level and the cursor visibility when the game is paused. Additionally, this included the development of the pause screen into the player prefab - it also being toggled on and off. The game can be paused with the use of the ESC key. Once paused, a user can either resume playing by using ESC again or making use of the button on screen. Furthermore, buttons were included on the top right side of the screen which allows a user to select which scene they wish to go to. Figure \ref{pause} shows the pause menu along with the associated buttons.

@@

\noindent The construction of the pause menu, other than the script was directly added to the player prefab in the form of images and text overlays. These were then linked to the functions in the script which handled all the various buttons shown. Figure \ref{pause2} illustrates the relations and links needed for the pause menu - it also shows most of the player prefab configuration.

\begin{figure}[H]
\centering
\includegraphics[scale=1]{Figures/pause2.png}
\caption{Pause Menu}
\label{pause2}
\end{figure}
